### 2015-02-11 README.Rmd
Added plot functionality to README.Rmd

#We're clearly missing some interesting data, but we can still 
#perform some analysis.
data(safety)

plot_safety(first_qmj, safety)

#Now let's look at a graph for quality.
data(quality)
second_qmj <- qmjs[[2]]

plot_quality(second_qmj, quality)

#What if I'm only interested in looking closely at a few companies? 
#Well, voila.
desired_companies <- c("GOOG", "IBM", "FLWS") #Returns a list containing the given qmj objects in order.
desired_qmjs <- get_qmjs(desired_companies, qmjs)

>>>>

#We're clearly missing some interesting data, but we can still 
#perform some analysis.
data(safety)
```
```{r simpleplot}
plot_safety(first_qmj, safety)
```

```{r}
#Now let's look at a graph for quality.
data(quality)
second_qmj <- qmjs[[2]]
```
```{r simpleplot}
plot_quality(second_qmj, quality)
```

```{r}
#What if I'm only interested in looking closely at a few companies? 
#Well, voila.
desired_companies <- c("GOOG", "IBM", "FLWS") #Returns a list containing the given qmj objects in order.
desired_qmjs <- get_qmjs(desired_companies, qmjs)
